Hierarchical Inference of the Intrinsic Ellipticity Distribution of Galaxies during Weak Lensing Analysis

### 2013-04-03 docs/ms.tex
Update ms.tex

A typical procedure of weak lensing analysis  includes ellipticity
measurement,shear inference and mass profile reconstruction. The measurement
of galaxy shapes is the first step of weak gravitational lensing analysis,since
it's the direct observable that relates with tangential shear.However
in this paper we only concern about how to infere shear from galaxy
ellipticity in a hierachical way.Therefore in our simulation we set
up a simple toy model in which we have the observed ellipticity as
data,and the only measurement error we consider is a Gaussian noise
added on the lensed galaxy ellipticity.We also suppose there is a uniform shear
acting on one all the galaxies in sky patch,

Our approach is to use an exceedingly flexible model for intrinsic
shape distribution,and assumes all the galaxies in different patches
abeys such a distribution.Then we can calculate the joint likelihood
of shpape distribution parameters and shear in differ shy patches.With
a classical Gibbs MCMC sampler we are able to sample their posteior
distriibution.After marginalizing the shape parameters, we can obtain
the posterior distribution of shear,which we are interested in.This
approach allows us use the information maximumly without introducing
in any wrong assumptions on intrinsic shape distribution.

>>>>

A typical procedure of weak lensing analysis  includes ellipticity
measurement,shear inference and mass profile reconstruction. The measurement
of galaxy shapes is the first step of weak gravitational lensing analysis,since
it's the direct observable that relates with tangential shear.However
in this paper we only concern about how to infer shear from galaxy
ellipticity in a hierachical way.Therefore in our simulation we merely
set up a simple toy model in which we have the observed ellipticity as
data,and the only measurement error we consider is a Gaussian noise
added on the lensed galaxy ellipticity.We also suppose there is a uniform shear
acting on one all the galaxies in sky patch,

Our approach is to use an exceedingly flexible model for intrinsic
shape distribution,and assumes all the galaxies in different patches
abeys such a distribution.Then we can calculate the joint likelihood
of shpape distribution parameters and shears in different sky patches.With
a classical Gibbs MCMC sampler we are able to sample their posteior
distriibution.After marginalizing the shape parameters, we can obtain
the posterior distribution of shear,which we are interested in.This
approach allows us use the information maximumly without introducing
in any wrong assumption on intrinsic shape distribution.
